Carbonate chemistry at Ny-Ålesund

### 2021-04-01 awipev-CO2.Rmd
cleaned up unnecessary packages

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("ragg")
library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")

@@

#### plot
kk <- melt(calib_spectro, id.vars="deployment_sf")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
  facet_grid(variable~., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
# if (!require("robfilter")) install.packages("robfilter")
# library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
# if (!require("reshape2")) install.packages("reshape2")
# library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
# if (!require("lmtest")) install.packages("lmtest")
# library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
# if (!require("seismicRoll")) install.packages("seismicRoll")
# library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
# if (!require("cowplot")) install.packages("cowplot")
# library(cowplot)
# if (!require("htmlwidgets")) install.packages("htmlwidgets")
# library("htmlwidgets")
# if (!require("hms")) install.packages("hms")
# library("hms")
# if (!require("ragg")) install.packages("ragg")
# library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")

@@

#### plot
kk <- tidyr::pivot_longer(calib_spectro, cols = starts_with("E0"), names_to = "variable", values_to = "value")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
  facet_grid(variable ~ ., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```
